Title Goes Here

### 2023-10-31 paper/main.tex
prior work WIP

[ computer proofs of MPC paper; (double-check malicions case...)
  l-obliv
  wysteria et al
  probabilistic separation logic]
\subsection{Verification of MPC}

[Computer-aided proofs for multiparty computation with active security](https://arxiv.org/pdf/1806.07197.pdf)

\subsection{Languages built inside of MPC implementations}

@@

dice

\subsection{PPL proof assistants}

lilac

>>>>

\subsection{Formal-methods for cryptography}
Although a useful language-driven test for MPC security remains out of reach,
a variety of useful work aproaches the subject from different directions.

\cite{https://arxiv.org/pdf/1806.07197.pdf} % Computer-aided proofs for multiparty computation with active security
use EasyCrypt to manually show the security of GMW.
Their definitions generalize to protocols with efficiently invertible functionalities.
% remove? Since existing general-purpose SMPC protocols can easily compute non-invertible functions, this is a serious limitation.
They model SMPC as a non-interference property: Honest secrets are non-interfering on the corrupt views conditioned on the corrupt outputs.
If their system could be automated and paired with language constraints to ensure invertibility then it
could apply to many, but certainly not all, use cases.

\cite{Barth et al} % https://arxiv.org/abs/1907.10708 A Probabilistic Separation Logic
give a framework for probabilistic reasoning and show that it can be used to prove security of additive secret sharing.
Even if the technique could be automated, it's unclear how it would generalize to any other kind of protocol.

\cite{Wysteria} % https://www.ieee-security.org/TC/SP2014/papers/Wysteria_c_AProgrammingLanguageforGeneric,Mixed-ModeMultipartyComputations.pdf
give fine-grain integration of MPC as a language primitive, to help a larger program use it efficiently.
[TODO: there are other/later works along these lines we should cite?]

\cite{lambda-obliv} %
gives a type system that ensures uniform and independent randomness of key values throughout a program.
Their system could be adapted to ensure perfect uniformity of parties' views in a protocol,
but this would of course prevent any non-vacuous functionality from being implemented.

@@

We experimented with choreography languages that translate directly into Sum Product Networks (SPNs) \cite{TODO}.
A SPN is directed-graph representation of a multi-variate distribution;
they are compact, allow efficient inference, and can represent values symbolically as needed,
so testing for conditional independence is practical.
However, such a language cannot express any existing MPC protocols, and likely cannot express any \textit{useful} protocols,
because if the language allowed any value to be used more than once, it would result in graphs that violate key invariants of SPNs.

The \cite{DICE} language analogously translates programs into binary decision diagrams (BDDs).
BDDs can represent, and do inference on, distributions that aren't representable as SPNs,
but since the graph \textit{structure} of the BDD of a DICE program depends on the actual \textit{values} on which one is conditioning,
a dice-based test for the kind of conditional independence needed for MPC would scale exponentially with the input/output width of the protocol.

\cite{lilac} % https://arxiv.org/abs/2304.01339
is a proof-assistant system for reasoning about probability distributions and PPLs.
It
